```{r}
#install.packages("reactablefmtr")
#install.packages("ggpbur")
#install.packages("caret")
library(ggpubr)
library(ggplot2)
library(plotly)
library(mosaic)
library(ggthemes)
library(reactable)
library(htmltools)
library(reactablefmtr)
library(tidyr)
library(dplyr)
library("FactoMineR")
library("factoextra")
library(glmnet)
library(caret)
```



```{r}
load("piracydf.RData")
load("piracyfactors.RData")
load("piracy.allfactors.RData")
load("content.RData")
options(scipen = 999)
```

```{r}
piracy.df$Piracy_use <- as.factor(piracy.df$Piracy_use)
```


# Explanatory Data Analysis

## Content Availability

### Difference in Means between Piracy and Non-Piracy Available Content

```{r}
piracy.df %>%
  mutate(Piracy_use = recode_factor(Piracy_use, "1" = "Pirate", "0" = "Non-Pirate")) %>%
  favstats(~content_avail | Piracy_use, data=.) %>%
  reactable(., highlight = TRUE, #allow for row to highlight when selected
          bordered = TRUE, #include borders between cells
          striped = TRUE, #striped rows
          compact = TRUE, # thinner rows
  #adjust table font
  theme = reactableTheme( style = list(fontFamily = "-system-ui, -apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif")))


```
#### Normality

```{r}
options(scipen = 999)
```


```{r}

piracy.df %>%
  filter(Piracy_use == 1) %>%
  ggplot(., aes(x = content_avail)) + geom_histogram(aes(y = ..density..), 
  bins = 10, fill = "skyblue", color = "black", alpha = 0.7) + geom_density(color = "red", size = 1) + xlab("Content Availability") + theme_stata() + ggtitle("Normality of Content Availability Amongst Pirates")


piracy.df %>%
  filter(Piracy_use == 0) %>%
  ggplot(., aes(x = content_avail)) + geom_histogram(aes(y = ..density..), 
  bins = 10, fill = "skyblue", color = "black", alpha = 0.7) + geom_density(color = "red", size = 1) + xlab("Content Availability") + theme_stata() + ggtitle("Normality of Content Availability Amongst Non-Pirates")
```



```{r}
# Shapiro-Wilk normality test for pirates
with(piracy.df, shapiro.test(content_avail[Piracy_use == 1]))# p = 0.1
# Shapiro-Wilk normality test for non-pirates
with(piracy.df, shapiro.test(content_avail[Piracy_use == 0])) # p = 0.6

```

**Non Normal but N>25**

#### Boxplot
https://r-graph-gallery.com/histogram_several_group.html
```{r}

p <- piracy.df %>%
  mutate(Piracy_use = recode_factor(Piracy_use, "1" = "Pirate", "0" = "Non-Pirate")) %>%
  ggboxplot(., x = "Piracy_use", y = "content_avail",
          color = "Piracy_use", palette = c("#00AFBB", "#E7B800"),
        ylab = "Content Availability", xlab = "Piracy Use")  + theme_stata() + ggtitle("Content Availability and Piracy Use") + theme(legend.position="none")
  

ggplotly(p) 
```

#### T.Test
```{r}
var.test(content_avail ~ Piracy_use, data = piracy.df)
t.test(content_avail ~ Piracy_use, data = piracy.df, var.equal = FALSE)
```
The mean average amount of content available to piraters and non-piraters is the same

### Difference in Means between Piracy and Non-Piracy between the Sexes

#### Boxplot

```{r}

piracy.df %>%
  mutate(Piracy_use = recode_factor(Piracy_use, "1" = "Pirate", "0" = "Non-Pirate")) %>%
  mutate(Sex = as.factor(Sex)) %>%
  mutate(Sex = recode_factor(Sex, "1" = "Male", "2" = "Female")) %>%
  ggboxplot(., x = "Piracy_use", y = "content_avail",
          color = "Sex", palette = c("#6F8FAF", "#FFC0CB"),
        ylab = "Content Availability", xlab = "Piracy Use")  + theme_stata() + ggtitle("Content Availability and Piracy Use - Sex")
```


```{r}
# Shapiro-Wilk normality test for Piracy's weights
with(piracy.df, shapiro.test(Sex[Piracy_use == 1]))# p = 0.1

# Shapiro-Wilk normality test for Non-Piracy's weights
with(piracy.df, shapiro.test(Sex[Piracy_use == 0]))
```
n>25 so can assume normality

```{r}
piracy.df %>%
  filter(Sex == 1) %>%
  var.test(content_avail ~ Piracy_use, data = .)


piracy.df %>%
  filter(Sex == 2) %>%
  var.test(content_avail ~ Piracy_use, data = .)
```
no significant difference between the variance

#### T.Test

```{r}
piracy.df %>%
  filter(Sex == 1) %>%
  t.test(content_avail ~ Piracy_use, data = ., var.equal = FALSE)


piracy.df %>%
  filter(Sex == 2) %>%
  t.test(content_avail ~ Piracy_use, data = ., var.equal = FALSE)
```

No difference in interest level between those who pirate and those who don't


### Difference in Means between Piracy and Non-Piracy between the Education

#### Boxplot

```{r}

piracy.df %>%
  mutate(Piracy_use = recode_factor(Piracy_use, "1" = "Pirate", "0" = "Non-Pirate")) %>%
  mutate(Education = as.factor(Education)) %>%
  mutate(Education = recode_factor(Education, "1" = "Primary", "2" = "Seconday", "3" = "Tertiary")) %>%
  ggboxplot(., x = "Piracy_use", y = "content_avail",
          color = "Education", palette = c("#233d4d", "#fe7f2d","#fcca46"),
        ylab = "Content Availability", xlab = "Piracy Use")  + theme_stata() + ggtitle("Content Availability - Education - Piracy Use") 
```
#### T.Test
```{r}

## Variance
piracy.df %>%
  filter(Education == 1) %>%
  var.test(content_avail ~ Piracy_use, data = .)

piracy.df %>%
  filter(Education == 2) %>%
  var.test(content_avail ~ Piracy_use, data = .)

piracy.df %>%
  filter(Education == 3) %>%
  var.test(content_avail ~ Piracy_use, data = .)

## Actual Test

piracy.df %>%
  t.test(content_avail ~ Piracy_use, data = ., var.equal = TRUE)

piracy.df %>%
  filter(Education == 1) %>%
  t.test(content_avail ~ Piracy_use, data = ., var.equal = TRUE)

piracy.df %>%
  filter(Education == 2) %>%
  t.test(content_avail ~ Piracy_use, data = ., var.equal = TRUE)

piracy.df %>%
  filter(Education == 3) %>%
  t.test(content_avail ~ Piracy_use, data = ., var.equal = FALSE)


## Further Tests

piracy.df %>%
  filter(Education == 1) %>%
  t.test(content_avail ~ Piracy_use, data = ., var.equal = FALSE, alternative = "greater")

piracy.df %>%
  filter(Education == 3) %>%
  t.test(content_avail ~ Piracy_use, data = ., var.equal = FALSE, alternative = "less")
```
When looking specifically at individuals that have a primary education, there is a difference between the amount of content piraters and non-piraters are. Non-piraters on average have access to more content than pirates

When looking specifically at individuals that have a tertiary education, there is a difference between the amount of content piraters and non-piraters are. Non-pirates on average has access to less content that pirates


### Difference in Means between Piracy and Non-Piracy between the Age

#### Boxplot

```{r}

piracy.df %>%
  mutate(Piracy_use = recode_factor(Piracy_use, "1" = "Pirate", "0" = "Non-Pirate")) %>%
  mutate(Age = as.factor(Age)) %>%
  mutate(Age = recode_factor(Age, "1" = "16-30", "2" = "31-40", "3" = "41-50", "4" = "51+")) %>%
  ggboxplot(., x = "Piracy_use", y = "content_avail",
          color = "Age", palette = c("#efd6ac", "#e07a5f","#3d405b","#81b29a"),
        ylab = "Content Availability", xlab = "Piracy Use")  + theme_stata() + ggtitle("Content Availability - Age - Piracy Use") 

```

#### T.Test

```{r}

## Variance
piracy.df %>%
  filter(Age == 1) %>%
  var.test(content_avail ~ Piracy_use, data = .)

piracy.df %>%
  filter(Age == 2) %>%
  var.test(content_avail ~ Piracy_use, data = .)

piracy.df %>%
  filter(Age == 3) %>%
  var.test(content_avail ~ Piracy_use, data = .)

piracy.df %>%
  filter(Age == 4) %>%
  var.test(content_avail ~ Piracy_use, data = .)

## Actual Test

piracy.df %>%
  t.test(content_avail ~ Piracy_use, data = ., var.equal = TRUE)

piracy.df %>%
  filter(Age == 1) %>%
  t.test(content_avail ~ Piracy_use, data = ., var.equal = TRUE)

piracy.df %>%
  filter(Age == 2) %>%
  t.test(content_avail ~ Piracy_use, data = ., var.equal = FALSE)

piracy.df %>%
  filter(Age == 3) %>%
  t.test(content_avail ~ Piracy_use, data = ., var.equal = FALSE)

piracy.df %>%
  filter(Age == 4) %>%
  t.test(content_avail ~ Piracy_use, data = ., var.equal = FALSE)

```

# Platform Usage

## Number of Users per Platform

```{r}

content.df %>%
  arrange(NumUsers) %>%
  mutate(provider = factor(provider, levels=provider)) %>%
  ggplot(aes(x=provider, y=NumUsers, fill = provider, label = NumUsers)) + 
  geom_bar(stat = "identity") +
  coord_flip() +
  ylab("") +
  xlab("Platforms") +
  ggtitle("Number of Users per Platform") + theme_stata() +  theme(axis.text.y = element_text(angle = 0, hjust = 1)) + 
  theme(legend.position="none", plot.title = element_text(hjust = 0.5)) + geom_label()


```



## Proportion of Piraters per Platform

```{r}
content.df %>%
  filter(NumUsers > 0) %>%
  arrange(PiratingUsers/NumUsers) %>%
  mutate(provider = factor(provider, levels=provider)) %>%
  ggplot(aes(x=provider, y=PiratingUsers/NumUsers, fill = provider, label=round(PiratingUsers/NumUsers,2))) + 
  geom_bar(stat = "identity") +  scale_fill_brewer(palette = "Paired") +
  coord_flip() +
  ylab("") +
  xlab("Platforms") +
  ggtitle("Proportion of Users per Platform that Pirate") + 
  theme_stata() + 
  theme(axis.text.y = element_text(angle = 0, hjust = 1)) + 
  geom_label() +
  theme(legend.position="none", plot.title = element_text(hjust = 0.5)) 
```


```{r}
top10factors <- piracy_factor %>%
  select(allplatforms) %>%
  group_by(allplatforms) %>%
  summarise(count = n()) %>%
  filter(count >= 20) %>%
  arrange(desc(count)) %>%
  select(allplatforms) %>%
  as.vector(.)
```


```{r}
atleast5factors <- piracy_factor %>%
  select(allplatforms, Piracy_use) %>%
  group_by(allplatforms, Piracy_use) %>%
  summarise(count = n()) %>%
  pivot_wider(values_from = count, names_from = Piracy_use) %>%
  filter(`Non-Pirate` > 4 & Pirate > 4) %>%
  select(allplatforms) %>%
  as.vector(.)
```


## Chi Squared Test
```{r}
## All Rows
chisq.test(piracy_factor$allplatforms, piracy_factor$Piracy_use, simulate.p.value = TRUE)

# Filtered Rows
temp <- piracy_factor %>%
  filter(allplatforms %in% top10factors$allplatforms)

chisq.test(temp$allplatforms, temp$Piracy_use)

rm(temp)

# At Least 5 factors

temp <- piracy_factor %>%
  filter(allplatforms %in% atleast5factors$allplatforms)

chisq.test(temp$allplatforms, temp$Piracy_use)

rm(temp)
        
```

## Proportion Table - Just Platforms
```{r}
p <- piracy_factor %>%
  filter(allplatforms %in% top10factors$allplatforms) %>%
  select(allplatforms) %>%
  mutate(allplatforms = as.factor(allplatforms)) %>% 
  table(.) %>%
  prop.table(.)

temp <- as.data.frame(p)

p <- temp %>%
  group_by(allplatforms) %>%
  summarise(`Proportion of Participants` = sum(Freq)) %>%
  ggplot(.) +
  geom_bar(aes(x = reorder(allplatforms, `Proportion of Participants`), y = `Proportion of Participants`, fill = allplatforms,
               text = paste0(
                 "Proportion: ", round(`Proportion of Participants`, 3),
                 "<br>",
                 "Platform Combination: ", allplatforms)), 
           stat = "identity", show.legend = FALSE) + 
  coord_flip() + xlab("Platform Combinations") + ggtitle("Proportion of Participants Subscribed to Platform Combinations") +
  theme_stata() + theme(axis.text.y = element_text(angle = 0, hjust = 1)) + theme(legend.position="none") 

ggplotly(p, tooltip = "text")

temp %>%
  rename(`Proportion of Participants` = Freq) %>%
  rename(`Platform Combinations` = allplatforms) %>%
  arrange(desc(`Proportion of Participants`)) %>%
  mutate(`Proportion of Participants` = round(`Proportion of Participants`, 3)) %>%
  reactable(., highlight = TRUE, #allow for row to highlight when selected
          bordered = TRUE, #include borders between cells
          striped = TRUE, #striped rows
          compact = TRUE, # thinner rows
  #adjust table font
  theme = reactableTheme( style = list(fontFamily = "-system-ui, -apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif")))

rm(temp)

```


## Proportion Table - Row Wise

```{r}
temp <- piracy_factor %>%
  filter(allplatforms %in% top10factors$allplatforms) %>%
  select(Piracy_use, allplatforms) %>%
  mutate(Piracy_use = as.factor(Piracy_use)) %>%
  mutate(allplatforms = as.factor(allplatforms)) %>% 
  table(.)

temp <- as.data.frame(prop.table(temp,2))

temp <- temp %>%
  mutate(content_avail = case_when(
    allplatforms == "Netflix" ~ 3411,
    allplatforms == "Amazon" ~ 3920,
    allplatforms == "Netflix, Amazon" ~ 7311,
    allplatforms == "Netflix, HboMax, Amazon, Disney" ~ 9907,
    allplatforms == "Netflix, Amazon, Disney" ~ 8973,
    allplatforms == "Netflix, HboMax, Amazon" ~ 8265,
    allplatforms == "Netflix, Disney" ~ 5053,
    allplatforms == "Non" ~ 0,
    allplatforms == "Amazon, Disney" ~ 5562,
    allplatforms == "Netflix, HboMax, Amazon, Disney, Apple" ~ 17544
  ))


```


```{r}

p <- temp %>%
  arrange(desc(content_avail)) %>%
  ggplot(., aes(x = allplatforms, y = Freq, fill = Piracy_use,
                text = paste0(
                "Proportion: ", round(Freq, 3),
                "<br>",
                "Content Availability: ", content_avail,
                "<br>",
                "Platform Combination: ", allplatforms))) +
  geom_bar(stat = "identity", position=position_dodge()) + coord_flip() +
  xlab("Platform Combinations") + ylab("Proportion of Participants") +
  theme_stata() + theme(axis.text.y = element_text(angle = 0, hjust = 1)) +
  ggtitle("Proportion of Piracy per Platform Combinations") + scale_fill_manual(values=c("#E7B800", "#00AFBB")) +
  labs(fill = "Piracy Use")

ggplotly(p, tooltip = "text")


temp %>%
  rename(`Platform Combinations` = allplatforms) %>%
  pivot_wider(values_from = Freq, names_from = Piracy_use) %>%
  mutate(Pirate = round(Pirate, 3)) %>%
  mutate(`Non-Pirate` = round(`Non-Pirate`, 3)) %>%
  reactable(., highlight = TRUE, #allow for row to highlight when selected
          bordered = TRUE, #include borders between cells
          striped = TRUE, #striped rows
          compact = TRUE, # thinner rows
  #adjust table font
  theme = reactableTheme( style = list(fontFamily = "-system-ui, -apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif")))

```



## Sex & Platform Combination

### Chi Squared Test 

```{r}
chisq.test(piracy_factor$allplatforms, piracy_factor$Sex, simulate.p.value = TRUE)
```
No relationship between Sex and Platforms Subscribed to

## Age & Platform Combination

### Chi Squared Test 

```{r}
temp <- piracy_factor %>%
  filter(allplatforms %in% top10factors$allplatforms) 
chisq.test(temp$allplatforms, temp$Age, simulate.p.value = TRUE)
```
There is a relationship between age and the platforms people use


### Plotting

```{r}

piracy_factor %>%
  filter(allplatforms == "Amazon") %>%
  select(allplatforms, Age, Piracy_use) %>%
  group_by(allplatforms, Age, Piracy_use) %>%
  summarise(count = n()) %>%
  pivot_wider(values_from = count, names_from = Piracy_use) %>%
  mutate(`Non-Pirate` = ifelse(is.na(`Non-Pirate`),0,`Non-Pirate`)) %>%
  mutate(Pirate = ifelse(is.na(Pirate),0,Pirate)) %>%
  mutate(`Proportion of Pirates` = as.numeric(round(Pirate/(Pirate+`Non-Pirate`),2))) %>%
  mutate(`Proportion of Non-Pirates` = as.numeric(round(`Non-Pirate`/(Pirate+`Non-Pirate`),2))) %>%
  select(allplatforms, Age, `Proportion of Pirates`, `Proportion of Non-Pirates`) %>%
  group_by(allplatforms) %>%
  reactable(., highlight = TRUE, #allow for row to highlight when selected
          bordered = TRUE, #include borders between cells
          striped = TRUE, #striped rows
          compact = TRUE, # thinner rows
          columns = list( 
            allplatforms = colDef(name = "Platform Combinations",
                                  minWidth = 100),
            Age = colDef(minWidth = 50),
            `Proportion of Pirates` = colDef(minWidth = 100),
            `Proportion of Non-Pirates` = colDef(minWidth = 100)),
  #adjust table font
  theme = reactableTheme( style = list(fontFamily = "-system-ui, -apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif")))

piracy_factor %>%
  filter(allplatforms %in% top10factors$allplatforms) %>%
  select(allplatforms, Age, Piracy_use) %>%
  group_by(allplatforms, Age, Piracy_use) %>%
  summarise(count = n()) %>%
  pivot_wider(values_from = count, names_from = Piracy_use) %>%
  mutate(`Non-Pirate` = ifelse(is.na(`Non-Pirate`),0,`Non-Pirate`)) %>%
  mutate(Pirate = ifelse(is.na(Pirate),0,Pirate)) %>%
  mutate(PP = Pirate/(Pirate+`Non-Pirate`)) %>%
  mutate(PNP = `Non-Pirate`/(Pirate+`Non-Pirate`)) %>%
  select(allplatforms, Age, PP, PNP) %>%
  pivot_longer(cols = c('PP','PNP'),
               names_to = "Piracy Use",
               values_to = "Proportion of Participants") %>%
  ggplot(., aes(x = allplatforms, y = `Proportion of Participants`, fill = `Piracy Use`))  + geom_bar(stat = "identity", position=position_dodge()) + coord_flip() + facet_wrap(~Age, dir = "v") + theme_stata() + scale_fill_manual(labels = c("Non-Pirate", "Pirate"), values=c("#E7B800", "#00AFBB")) + theme(axis.text.y = element_text(angle = 0, hjust = 1)) 


  
piracy_factor %>%
  filter(allplatforms %in% top10factors$allplatforms) %>%
  select(allplatforms, Age, Piracy_use) %>%
  group_by(allplatforms, Age, Piracy_use) %>%
  summarise(count = n()) %>%
  pivot_wider(values_from = count, names_from = Piracy_use) %>%
  mutate(`Non-Pirate` = ifelse(is.na(`Non-Pirate`),0,`Non-Pirate`)) %>%
  mutate(Pirate = ifelse(is.na(Pirate),0,Pirate)) %>%
  mutate(PP = Pirate/(Pirate+`Non-Pirate`)) %>%
  mutate(PNP = `Non-Pirate`/(Pirate+`Non-Pirate`)) %>%
  select(allplatforms, Age, PP, PNP) %>%
  pivot_longer(cols = c('PP','PNP'),
               names_to = "Piracy Use",
               values_to = "Proportion of Participants") %>%
  ggplot(., aes(x = Age, y = `Proportion of Participants`, fill = `Piracy Use`))  + geom_bar(stat = "identity", position=position_dodge()) + coord_flip() + facet_wrap(~allplatforms, dir = "v") + theme_stata() + scale_fill_manual(labels = c("Non-Pirate", "Pirate"), values=c("#E7B800", "#00AFBB")) + theme(axis.text.y = element_text(angle = 0, hjust = 1))


```




## Education & Platform Combination

### Chi Squared Test 

```{r}
chisq.test(piracy_factor$allplatforms, piracy_factor$Education, simulate.p.value = TRUE)
```
There is no relationship between education and platforms people use


# Age

## Chi Squared Test
```{r}
chisq.test(piracy.df$Age, piracy.df$Piracy_use)
```
Is a relationship between age and piracy


## Mosaic Plot
```{r}
piracy.df %>%
  select(Age, Piracy_use) %>%
  table(.) %>%
  mosaicplot(.)
```



## Plotting
```{r}
piracy_factor %>%
  select(Age, Piracy_use) %>%
  group_by(Age, Piracy_use) %>%
  summarise(count = n(), .groups = "drop") %>%
  pivot_wider(values_from = count, names_from = Piracy_use) %>%
  mutate(`Non-Pirate` = ifelse(is.na(`Non-Pirate`), 0, `Non-Pirate`)) %>%
  mutate(Pirate = ifelse(is.na(Pirate), 0, Pirate)) %>%
  mutate(Total = Pirate + `Non-Pirate`) %>%
  mutate(`Proportion of Pirates` = round(Pirate / Total, 2)) %>%
  mutate(`Proportion of Non-Pirates` = round(`Non-Pirate` / Total, 2)) %>%
  ungroup() %>%
  mutate(Total_All = sum(Total)) %>%
  mutate(`Proportion of Age Group` = round(Total / Total_All, 2)) %>%
  select(Age, `Proportion of Pirates`, `Proportion of Non-Pirates`,`Proportion of Age Group`) %>%
  reactable(
    .,
    highlight = TRUE,
    bordered = TRUE,
    striped = TRUE,
    compact = TRUE,
    columns = list(
      Age = colDef(minWidth = 50),
      `Proportion of Pirates` = colDef(minWidth = 100),
      `Proportion of Non-Pirates` = colDef(minWidth = 100),
      `Proportion of Age Group` = colDef(minWidth = 100)
    ),
    theme = reactableTheme(style = list(fontFamily = "-system-ui, -apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif")))


p <- piracy_factor %>%
  select(Age, Piracy_use) %>%
  group_by(Age, Piracy_use) %>%
  summarise(count = n(), .groups = "drop") %>%
  pivot_wider(values_from = count, names_from = Piracy_use) %>%
  mutate(`Non-Pirate` = ifelse(is.na(`Non-Pirate`), 0, `Non-Pirate`)) %>%
  mutate(Pirate = ifelse(is.na(Pirate), 0, Pirate)) %>%
  mutate(Total = Pirate + `Non-Pirate`) %>%
  mutate(`Proportion of Pirates` = round(Pirate / Total, 2)) %>%
  mutate(`Proportion of Non-Pirates` = round(`Non-Pirate` / Total, 2)) %>%
  ungroup() %>%
  mutate(Total_All = sum(Total)) %>%
  mutate(`Proportion of Age Group` = round(Total / Total_All, 2)) %>%
  select(Age, `Proportion of Pirates`, `Proportion of Age Group`) %>%
  arrange(`Proportion of Age Group`) %>%
  ggplot(., aes(x = Age, y = `Proportion of Pirates`, fill = Age,
                text = paste0(
                "Proportion of Pirates per Age Group: ", round(`Proportion of Pirates`, 3),
                "<br>",
                "Proportion of Demographic: ", `Proportion of Age Group`,
                "<br>",
                "Age Group: ", Age))) +
  geom_bar(stat = "identity", position=position_dodge()) + coord_flip() +
  xlab("Age Group") + ylab("Proportion of Participants") +
  theme_stata() + theme(axis.text.y = element_text(angle = 0, hjust = 1)) +
  ggtitle("Proportion of Pirates per Age Group") 

ggplotly(p, tooltip = "text")
  

```

# Education

## Chi Squared Test

```{r}
chisq.test(piracy.df$Education, piracy.df$Piracy_use)
```

## Table
```{r}

piracy_factor %>%
  select(Education, Piracy_use) %>%
  group_by(Education, Piracy_use) %>%
  summarise(count = n(), .groups = "drop") %>%
  pivot_wider(values_from = count, names_from = Piracy_use) %>%
  mutate(Total = Pirate + `Non-Pirate`) %>%
  mutate(`Proportion of Pirates` = round(Pirate / Total, 2)) %>%
  mutate(`Proportion of Non-Pirates` = round(`Non-Pirate` / Total, 2)) %>%
  ungroup() %>%
  mutate(Total_All = sum(Total)) %>%
  mutate(`Proportion of Demographic` = round(Total/Total_All,2)) %>%
  select(Education, `Proportion of Pirates`, `Proportion of Non-Pirates`, `Proportion of Demographic`) %>%
  reactable(., highlight = TRUE, #allow for row to highlight when selected
          bordered = TRUE, #include borders between cells
          striped = TRUE, #striped rows
          compact = TRUE, # thinner rows
          columns = list( 
            Education = colDef(minWidth = 50),
            `Proportion of Demographic` = colDef(minWidth = 100),
            `Proportion of Pirates` = colDef(minWidth = 100),
            `Proportion of Non-Pirates` = colDef(minWidth = 100)),
  #adjust table font
  theme = reactableTheme( style = list(fontFamily = "-system-ui, -apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif")))

  
```


## Graph
```{r}
piracy_factor %>%
  select(Education, Piracy_use) %>%
  group_by(Education, Piracy_use) %>%
  summarise(count = n(), .groups = "drop") %>%
  pivot_wider(values_from = count, names_from = Piracy_use) %>%
  mutate(Total = Pirate + `Non-Pirate`) %>%
  mutate(`Proportion of Pirates` = round(Pirate / Total, 2)) %>%
  mutate(`Proportion of Non-Pirates` = round(`Non-Pirate` / Total, 2)) %>%
  ungroup() %>%
  mutate(Total_All = sum(Total)) %>%
  mutate(`Proportion of Demographic` = round(Total/Total_All,2)) %>%
  select(Education, `Proportion of Pirates`, `Proportion of Non-Pirates`, `Proportion of Demographic`) %>%
  ggplot(., aes(x = Education, y = `Proportion of Demographic`, label = round(`Proportion of Demographic`,2), fill=Education)) + 
    geom_bar(stat = "identity", position=position_dodge()) + coord_flip() +
    xlab("Education") + ylab("Proportion of Participants") +
  theme_stata() + theme(axis.text.y = element_text(angle = 0, hjust = 1)) +
  ggtitle("Proportion of Participants per Education Level") + scale_fill_manual(values=c("#233d4d", "#fe7f2d","#fcca46")) + labs(fill = "Piracy Use") + geom_label()

```

## Graph Facets

```{r}
piracy_factor %>%
  select(Education, Piracy_use) %>%
  group_by(Education, Piracy_use) %>%
  summarise(count = n(), .groups = "drop") %>%
  pivot_wider(values_from = count, names_from = Piracy_use) %>%
  mutate(Total = Pirate + `Non-Pirate`) %>%
  mutate(`Proportion of Pirates` = round(Pirate / Total, 2)) %>%
  mutate(`Proportion of Non-Pirates` = round(`Non-Pirate` / Total, 2)) %>%
  ungroup() %>%
  mutate(Total_All = sum(Total)) %>%
  mutate(`Proportion of Demographic` = round(Total/Total_All,2)) %>%
  select(Education, `Proportion of Pirates`, `Proportion of Non-Pirates`) %>%
  pivot_longer(cols = c("Proportion of Pirates", "Proportion of Non-Pirates"),
               names_to = "Piracy Use", 
               values_to = "Proportion of Participants") %>%
  mutate(`Piracy Use` = recode_factor(`Piracy Use`, "Proportion of Pirates" = "Pirate", "Proportion of Non-Pirates" = "Non-Pirates")) %>%
  ggplot(., aes(x = Education, y = `Proportion of Participants`, fill = `Piracy Use`))  + geom_bar(stat = "identity", position=position_dodge()) + coord_flip() + theme_stata() + scale_fill_manual(labels = c("Non-Pirate", "Pirate"), values=c("#E7B800", "#00AFBB")) + theme(axis.text.y = element_text(angle = 0, hjust = 1)) + ggtitle("Proportional Piracy by Education Level")
# 
# 
#   
# piracy_factor %>%
#   filter(allplatforms %in% top10factors$allplatforms) %>%
#   select(allplatforms, Age, Piracy_use) %>%
#   group_by(allplatforms, Age, Piracy_use) %>%
#   summarise(count = n()) %>%
#   pivot_wider(values_from = count, names_from = Piracy_use) %>%
#   mutate(`Non-Pirate` = ifelse(is.na(`Non-Pirate`),0,`Non-Pirate`)) %>%
#   mutate(Pirate = ifelse(is.na(Pirate),0,Pirate)) %>%
#   mutate(PP = Pirate/(Pirate+`Non-Pirate`)) %>%
#   mutate(PNP = `Non-Pirate`/(Pirate+`Non-Pirate`)) %>%
#   select(allplatforms, Age, PP, PNP) %>%
#   pivot_longer(cols = c('PP','PNP'),
#                names_to = "Piracy Use",
#                values_to = "Proportion of Participants") %>%
#   ggplot(., aes(x = Age, y = `Proportion of Participants`, fill = `Piracy Use`))  + geom_bar(stat = "identity", position=position_dodge()) + coord_flip() + facet_wrap(~allplatforms, dir = "v") + theme_stata() + scale_fill_manual(labels = c("Non-Pirate", "Pirate"), values=c("#E7B800", "#00AFBB")) + theme(axis.text.y = element_text(angle = 0, hjust = 1))
```


# Sex

## Chi Squared Test
```{r}
chisq.test(piracy.df$Sex, piracy.df$Piracy_use)
```
## Plotting
```{r}

## Pirates 
piracy.df %>%
  select(Sex, Piracy_use) %>%
  mutate(Sex = as.factor(Sex)) %>%
  group_by(Sex) %>%
  count(Piracy_use) %>%
  mutate(Piracy_use = case_when(
    Piracy_use == 1 ~ "Pirate",
    Piracy_use == 0 ~ "NonPirate"
  )) %>%
    mutate(Sex = case_when(
    Sex == 1 ~ "Male",
    Sex == 2 ~ "Female"
  )) %>%
  pivot_wider(names_from = Piracy_use, values_from = n) %>%
  mutate(prop_pirate = Pirate/(Pirate+NonPirate))  %>%
  ggplot(.) + geom_bar(aes(x = Sex, y = prop_pirate, fill = Sex), stat="identity", position="dodge", na.rm=TRUE) + ggtitle("Proportional Piracy by Sex") + ylab("Proportion of Piraters")  + xlab("Sex") +  theme(legend.position="none", plot.title = element_text(hjust = 0.5)) 

##Non Pirates
piracy.df %>%
  select(Sex, Piracy_use) %>%
  mutate(Sex = as.factor(Sex)) %>%
  group_by(Sex) %>%
  count(Piracy_use) %>%
  mutate(Piracy_use = case_when(
    Piracy_use == 1 ~ "Pirate",
    Piracy_use == 0 ~ "NonPirate"
  )) %>%
    mutate(Sex = case_when(
    Sex == 1 ~ "Male",
    Sex == 2 ~ "Female"
  )) %>%
  pivot_wider(names_from = Piracy_use, values_from = n) %>%
  mutate(prop_pirate = NonPirate/(Pirate+NonPirate))  %>%
  ggplot(.) + geom_bar(aes(x = Sex, y = prop_pirate, fill = Sex), stat="identity", position="dodge", na.rm=TRUE) + ggtitle("Proportional Non-Piracy by Sex") + ylab("Proportion of Non-Piraters")  + xlab("Sex") +  theme(legend.position="none", plot.title = element_text(hjust = 0.5)) 

#Pirates and Non-Pirates
piracy_factor %>%
  select(Sex, Piracy_use) %>%
  group_by(Sex, Piracy_use) %>%
  summarise(count = n(), .groups = "drop") %>%
  pivot_wider(values_from = count, names_from = Piracy_use) %>%
  mutate(Total = Pirate + `Non-Pirate`) %>%
  mutate(`Proportion of Pirates` = round(Pirate / Total, 2)) %>%
  mutate(`Proportion of Non-Pirates` = round(`Non-Pirate` / Total, 2)) %>%
  ungroup() %>%
  mutate(Total_All = sum(Total)) %>%
  mutate(`Proportion of Demographic` = round(Total/Total_All,2)) %>%
  select(Sex, `Proportion of Pirates`, `Proportion of Non-Pirates`, `Proportion of Demographic`) %>%
  ggplot(., aes(x = Sex, y = `Proportion of Demographic`, label = round(`Proportion of Demographic`,2), fill=Sex)) + 
    geom_bar(stat = "identity", position=position_dodge()) + coord_flip() +
    xlab("Sex") + ylab("Proportion of Participants") +
  theme_stata() + theme(axis.text.y = element_text(angle = 0, hjust = 1)) +
  ggtitle("Proportion of Participants per Sex Level") + scale_fill_manual(values=c("#6F8FAF", "#FFC0CB")) + labs(fill = "Piracy Use") + geom_label()


##ggplotly
p <- piracy_factor %>%
  select(Sex, Piracy_use) %>%
  group_by(Sex, Piracy_use) %>%
  summarise(count = n(), .groups = "drop") %>%
  pivot_wider(values_from = count, names_from = Piracy_use) %>%
  mutate(Total = Pirate + `Non-Pirate`) %>%
  mutate(`Proportion of Pirates` = round(Pirate / Total, 2)) %>%
  mutate(`Proportion of Non-Pirates` = round(`Non-Pirate` / Total, 2)) %>%
  ungroup() %>%
  mutate(Total_All = sum(Total)) %>%
  mutate(`Proportion of Demographic` = round(Total/Total_All,2)) %>%
  select(Sex, `Proportion of Pirates`, `Proportion of Non-Pirates`) %>%
  pivot_longer(cols = c("Proportion of Pirates", "Proportion of Non-Pirates"),
               names_to = "Piracy Use", 
               values_to = "Proportion of Participants") %>%
  mutate(`Piracy Use` = recode_factor(`Piracy Use`, "Proportion of Pirates" = "Pirate", "Proportion of Non-Pirates" = "Non-Pirates")) %>%
  ggplot(., aes(x = Sex, y = `Proportion of Participants`, fill = `Piracy Use`))  + geom_bar(stat = "identity", position=position_dodge()) + coord_flip() + theme_stata() + scale_fill_manual(labels = c("Non-Pirate", "Pirate"), values=c("#E7B800", "#00AFBB")) + theme(axis.text.y = element_text(angle = 0, hjust = 1)) + ggtitle("Proportional Piracy by Sex Level")

ggplotly(p)
```

## Tables
```{r}
piracy_factor %>%
  select(Sex, Piracy_use) %>%
  group_by(Sex, Piracy_use) %>%
  summarise(count = n(), .groups = "drop") %>%
  pivot_wider(values_from = count, names_from = Piracy_use) %>%
  mutate(Total = Pirate + `Non-Pirate`) %>%
  mutate(`Proportion of Pirates` = round(Pirate / Total, 2)) %>%
  mutate(`Proportion of Non-Pirates` = round(`Non-Pirate` / Total, 2)) %>%
  ungroup() %>%
  mutate(Total_All = sum(Total)) %>%
  mutate(`Proportion of Demographic` = round(Total/Total_All,2)) %>%
  select(Sex, `Proportion of Pirates`, `Proportion of Non-Pirates`, `Proportion of Demographic`) %>%
  reactable(., highlight = TRUE, #allow for row to highlight when selected
          bordered = TRUE, #include borders between cells
          striped = TRUE, #striped rows
          compact = TRUE, # thinner rows
          columns = list( 
            Sex = colDef(minWidth = 50),
            `Proportion of Demographic` = colDef(minWidth = 100),
            `Proportion of Pirates` = colDef(minWidth = 100),
            `Proportion of Non-Pirates` = colDef(minWidth = 100)),
  #adjust table font
  theme = reactableTheme( style = list(fontFamily = "-system-ui, -apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif")))
```

# Genres

## Action

### Stats
```{r}

chisq.test(piracy.df$Interest_Action, piracy.df$Piracy_use)

piracy.df %>%
  select(Interest_Action, Piracy_use) %>%
  mutate(Interest_Action = ifelse(Interest_Action == 4 | Interest_Action == 5, "High", "Low")) %>%
  table(.) %>%
  fisher.test(.)


```
No statistically significant relationship between interest in Action and Piracy. 


### Mosaic Plot
```{r}
piracy.df %>%
  select(Interest_Action, Piracy_use) %>%
  mutate(Interest_Action = ifelse(Interest_Action == 4 | Interest_Action == 5, "High", "Low")) %>%
  table(.) %>%
  mosaicplot(.)
```

### Plotting
```{r}
piracy.df %>%
  select(Interest_Action, Piracy_use) %>%
  mutate(Interest_Action = as.factor(Interest_Action)) %>%
  group_by(Interest_Action, Piracy_use) %>%
  summarise(count = n()) %>%
  pivot_wider(values_from = count, names_from = Piracy_use) %>%
  mutate(Total = `0` + `1`) %>%
  mutate(`Proportion of Non-Pirates` = round((`0`/(`0`+`1`)),3)) %>%
  mutate(`Proportion of Pirates` = round((`1`/(`0`+`1`)),3)) %>%
  ungroup() %>%
  mutate(Total_All = sum(Total)) %>%
  mutate(`Proportion of Demographic` = round(Total/Total_All,3)) %>%
  select(Interest_Action,`Proportion of Demographic` ,`Proportion of Pirates`, `Proportion of Non-Pirates`)%>%
reactable(., highlight = TRUE, #allow for row to highlight when selected
          bordered = TRUE, #include borders between cells
          striped = TRUE, #striped rows
          compact = TRUE, # thinner rows
       
  #adjust table font
  theme = reactableTheme(style = list(fontFamily = "-system-ui, -apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif")))

piracy.df %>%
  select(Interest_Action, Piracy_use) %>%
  mutate(Interest_Action = as.factor(Interest_Action)) %>%
  group_by(Interest_Action, Piracy_use) %>%
  summarise(count = n()) %>%
  pivot_wider(values_from = count, names_from = Piracy_use) %>%
  mutate(`Proportion of Non-Pirates` = `0`/(`0`+`1`)) %>%
  mutate(`Proportion of Pirates` = `1`/(`0`+`1`)) %>%
  select(Interest_Action, `Proportion of Pirates`, `Proportion of Non-Pirates`) %>%
  pivot_longer(cols = c("Proportion of Pirates", "Proportion of Non-Pirates"),
                                                      names_to = "Piracy Use",
                                                      values_to = "Proportion of Participants") %>%
    ggplot(., aes(x = Interest_Action, y = `Proportion of Participants`, fill = `Piracy Use`))  + geom_col(stat = "identity", width = 0.5,  position=position_dodge(0.5)) + coord_flip() + theme_stata() + scale_fill_manual(labels = c("Non-Pirate", "Pirate"), values=c("#E7B800", "#00AFBB")) + theme(axis.text.y = element_text(angle = 0, hjust = 1)) + ggtitle("Proportional Piracy by Sex Level") + xlab("User Interest") 
  
```

```{r}
table(piracy.df$Interest_Action)
```


## Comedy

```{r}
table(piracy.df$Interest_Comedy)
```

### Mosaic Plot
```{r}
piracy.df %>%
  select(Interest_Comedy, Piracy_use) %>%
  table(.) %>%
  mosaicplot(.)


piracy.df %>%
  select(Interest_Comedy, Piracy_use) %>%
  mutate(Interest_Comedy = ifelse(Interest_Comedy == 4 | Interest_Comedy == 5, "High", "Low")) %>%
  table(.) %>%
  mosaicplot(.)


```


### Plotting

```{r}
piracy.df %>%
  select(Interest_Comedy, Piracy_use) %>%
  mutate(Interest_Comedy = as.factor(Interest_Comedy)) %>%
  group_by(Interest_Comedy, Piracy_use) %>%
  summarise(count = n()) %>%
  pivot_wider(values_from = count, names_from = Piracy_use) %>%
  mutate(Total = `0` + `1`) %>%
  mutate(`Proportion of Non-Pirates` = round((`0`/(`0`+`1`)),3)) %>%
  mutate(`Proportion of Pirates` = round((`1`/(`0`+`1`)),3)) %>%
  ungroup() %>%
  mutate(Total_All = sum(Total)) %>%
  mutate(`Proportion of Demographic` = round(Total/Total_All,3)) %>%
  select(Interest_Comedy,`Proportion of Demographic` ,`Proportion of Pirates`, `Proportion of Non-Pirates`)%>%
reactable(., highlight = TRUE, #allow for row to highlight when selected
          bordered = TRUE, #include borders between cells
          striped = TRUE, #striped rows
          compact = TRUE, # thinner rows
       
  #adjust table font
  theme = reactableTheme(style = list(fontFamily = "-system-ui, -apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif")))

piracy.df %>%
  select(Interest_Comedy, Piracy_use) %>%
  mutate(Interest_Comedy = as.factor(Interest_Comedy)) %>%
  group_by(Interest_Comedy, Piracy_use) %>%
  summarise(count = n()) %>%
  pivot_wider(values_from = count, names_from = Piracy_use) %>%
  mutate(`Proportion of Non-Pirates` = `0`/(`0`+`1`)) %>%
  mutate(`Proportion of Pirates` = `1`/(`0`+`1`)) %>%
  select(Interest_Comedy, `Proportion of Pirates`, `Proportion of Non-Pirates`) %>%
  pivot_longer(cols = c("Proportion of Pirates", "Proportion of Non-Pirates"),
                                                      names_to = "Piracy Use",
                                                      values_to = "Proportion of Participants") %>%
    ggplot(., aes(x = Interest_Comedy, y = `Proportion of Participants`, fill = `Piracy Use`))  + geom_col(stat = "identity", width = 0.5,  position=position_dodge(0.5)) + coord_flip() + theme_stata() + scale_fill_manual(labels = c("Non-Pirate", "Pirate"), values=c("#E7B800", "#00AFBB")) + theme(axis.text.y = element_text(angle = 0, hjust = 1)) + ggtitle("Proportional Piracy by Sex Level") + xlab("User Interest") 
  
```

### Stats

```{r}
chisq.test(piracy.df$Interest_Comedy, piracy.df$Piracy_use)


piracy.df %>%
  select(Interest_Comedy, Piracy_use) %>%
  mutate(Interest_Comedy = ifelse(Interest_Comedy == 4 | Interest_Comedy == 5, "High", "Low")) %>%
  table(.) %>%
  fisher.test(.)
```
No relationship between comedy and piracy


## Disaster

### Stats

```{r}
table(piracy.df$Interest_Disaster)

temp <- piracy.df %>%
  filter(Interest_Disaster != 1) 

chisq.test(temp$Interest_Disaster, temp$Piracy_use, simulate.p.value = TRUE)

rm(temp)

piracy.df %>%
  select(Interest_Disaster, Piracy_use) %>%
  mutate(Interest_Disaster = ifelse(Interest_Disaster == 4 | Interest_Disaster == 5 , "High", "Low")) %>%
  table(.) %>%
  fisher.test(.)

```
There is a relationship between disaster and piracy when 

### Mosaic Plot
```{r}
piracy.df %>%
  select(Interest_Disaster, Piracy_use) %>%
  table(.) %>%
  mosaicplot(.)


piracy.df %>%
  select(Interest_Disaster, Piracy_use) %>%
  mutate(Interest_Disaster = ifelse(Interest_Disaster == 4 | Interest_Disaster == 5, "High", "Low")) %>%
  table(.) %>%
  mosaicplot(.)
```


### Plotting

```{r}
piracy.df %>%
  select(Interest_Disaster, Piracy_use) %>%
  mutate(Interest_Disaster = as.factor(Interest_Disaster)) %>%
  group_by(Interest_Disaster, Piracy_use) %>%
  summarise(count = n()) %>%
  pivot_wider(values_from = count, names_from = Piracy_use) %>%
  mutate(Total = `0` + `1`) %>%
  mutate(`Proportion of Non-Pirates` = round((`0`/(`0`+`1`)),3)) %>%
  mutate(`Proportion of Pirates` = round((`1`/(`0`+`1`)),3)) %>%
  ungroup() %>%
  mutate(Total_All = sum(Total)) %>%
  mutate(`Proportion of Demographic` = round(Total/Total_All,3)) %>%
  select(Interest_Disaster,`Proportion of Demographic` ,`Proportion of Pirates`, `Proportion of Non-Pirates`)%>%
reactable(., highlight = TRUE, #allow for row to highlight when selected
          bordered = TRUE, #include borders between cells
          striped = TRUE, #striped rows
          compact = TRUE, # thinner rows
       
  #adjust table font
  theme = reactableTheme(style = list(fontFamily = "-system-ui, -apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif")))

piracy.df %>%
  select(Interest_Disaster, Piracy_use) %>%
  mutate(Interest_Disaster = as.factor(Interest_Disaster)) %>%
  group_by(Interest_Disaster, Piracy_use) %>%
  summarise(count = n()) %>%
  pivot_wider(values_from = count, names_from = Piracy_use) %>%
  mutate(`Proportion of Non-Pirates` = `0`/(`0`+`1`)) %>%
  mutate(`Proportion of Pirates` = `1`/(`0`+`1`)) %>%
  select(Interest_Disaster, `Proportion of Pirates`, `Proportion of Non-Pirates`) %>%
  pivot_longer(cols = c("Proportion of Pirates", "Proportion of Non-Pirates"),
                                                      names_to = "Piracy Use",
                                                      values_to = "Proportion of Participants") %>%
    ggplot(., aes(x = Interest_Disaster, y = `Proportion of Participants`, fill = `Piracy Use`))  + geom_col(stat = "identity", width = 0.5,  position=position_dodge(0.5)) + coord_flip() + theme_stata() + scale_fill_manual(labels = c("Non-Pirate", "Pirate"), values=c("#E7B800", "#00AFBB")) + theme(axis.text.y = element_text(angle = 0, hjust = 1)) + ggtitle("Proportional Piracy by Sex Level") + xlab("User Interest") 

```
## Documentary

### Stats

```{r}
table(piracy.df$Interest_Documentary)
```


```{r}

temp <- piracy.df %>%
  filter(Interest_Documentary != 1) 

chisq.test(temp$Interest_Documentary, temp$Piracy_use, simulate.p.value = TRUE)

rm(temp)

piracy.df %>%
  select(Interest_Documentary, Piracy_use) %>%
  mutate(Interest_Documentary = ifelse(Interest_Documentary == 4 | Interest_Documentary == 5 , "High", "Low")) %>%
  table(.) %>%
  fisher.test(.)
  
```


There is no relationship between documentary and piracy 



### Mosaic Plot
```{r}
piracy.df %>%
  select(Interest_Documentary, Piracy_use) %>%
  table(.) %>%
  mosaicplot(.)


piracy.df %>%
  select(Interest_Documentary, Piracy_use) %>%
  mutate(Interest_Documentary = ifelse(Interest_Documentary == 4 | Interest_Documentary == 5, "High", "Low")) %>%
  table(.) %>%
  mosaicplot(.)
```

### Plotting

```{r}
piracy.df %>%
  select(Interest_Documentary, Piracy_use) %>%
  mutate(Interest_Documentary = as.factor(Interest_Documentary)) %>%
  group_by(Interest_Documentary, Piracy_use) %>%
  summarise(count = n()) %>%
  pivot_wider(values_from = count, names_from = Piracy_use) %>%
  mutate(Total = `0` + `1`) %>%
  mutate(`Proportion of Non-Pirates` = round((`0`/(`0`+`1`)),3)) %>%
  mutate(`Proportion of Pirates` = round((`1`/(`0`+`1`)),3)) %>%
  ungroup() %>%
  mutate(Total_All = sum(Total)) %>%
  mutate(`Proportion of Demographic` = round(Total/Total_All,3)) %>%
  select(Interest_Documentary,`Proportion of Demographic` ,`Proportion of Pirates`, `Proportion of Non-Pirates`)%>%
reactable(., highlight = TRUE, #allow for row to highlight when selected
          bordered = TRUE, #include borders between cells
          striped = TRUE, #striped rows
          compact = TRUE, # thinner rows
       
  #adjust table font
  theme = reactableTheme(style = list(fontFamily = "-system-ui, -apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif")))

piracy.df %>%
  select(Interest_Documentary, Piracy_use) %>%
  mutate(Interest_Documentary = as.factor(Interest_Documentary)) %>%
  group_by(Interest_Documentary, Piracy_use) %>%
  summarise(count = n()) %>%
  pivot_wider(values_from = count, names_from = Piracy_use) %>%
  mutate(`Proportion of Non-Pirates` = `0`/(`0`+`1`)) %>%
  mutate(`Proportion of Pirates` = `1`/(`0`+`1`)) %>%
  select(Interest_Documentary, `Proportion of Pirates`, `Proportion of Non-Pirates`) %>%
  pivot_longer(cols = c("Proportion of Pirates", "Proportion of Non-Pirates"),
                                                      names_to = "Piracy Use",
                                                      values_to = "Proportion of Participants") %>%
    ggplot(., aes(x = Interest_Documentary, y = `Proportion of Participants`, fill = `Piracy Use`))  + geom_col(stat = "identity", width = 0.5,  position=position_dodge(0.5)) + coord_flip() + theme_stata() + scale_fill_manual(labels = c("Non-Pirate", "Pirate"), values=c("#E7B800", "#00AFBB")) + theme(axis.text.y = element_text(angle = 0, hjust = 1)) + ggtitle("Proportional Piracy by Sex Level") + xlab("User Interest") 
  
```



## Drama

### Stats

```{r}
table(piracy.df$Interest_Drama)
```


```{r}

chisq.test(piracy.df$Interest_Drama, piracy.df$Piracy_use)

piracy.df %>%
  select(Interest_Drama, Piracy_use) %>%
  mutate(Interest_Drama = ifelse(Interest_Drama == 4 | Interest_Drama == 5 , "High", "Low")) %>%
  table(.) %>%
  fisher.test(.)
  
```


There is no relationship between drama and piracy 



### Mosaic Plot
```{r}
piracy.df %>%
  select(Interest_Drama, Piracy_use) %>%
  table(.) %>%
  mosaicplot(.)


piracy.df %>%
  select(Interest_Drama, Piracy_use) %>%
  mutate(Interest_Drama = ifelse(Interest_Drama == 4 | Interest_Drama == 5, "High", "Low")) %>%
  table(.) %>%
  mosaicplot(.)
```

### Plotting

```{r}
piracy.df %>%
  select(Interest_Drama, Piracy_use) %>%
  mutate(Interest_Drama = as.factor(Interest_Drama)) %>%
  group_by(Interest_Drama, Piracy_use) %>%
  summarise(count = n()) %>%
  pivot_wider(values_from = count, names_from = Piracy_use) %>%
  mutate(Total = `0` + `1`) %>%
  mutate(`Proportion of Non-Pirates` = round((`0`/(`0`+`1`)),3)) %>%
  mutate(`Proportion of Pirates` = round((`1`/(`0`+`1`)),3)) %>%
  ungroup() %>%
  mutate(Total_All = sum(Total)) %>%
  mutate(`Proportion of Demographic` = round(Total/Total_All,3)) %>%
  select(Interest_Drama,`Proportion of Demographic` ,`Proportion of Pirates`, `Proportion of Non-Pirates`)%>%
reactable(., highlight = TRUE, #allow for row to highlight when selected
          bordered = TRUE, #include borders between cells
          striped = TRUE, #striped rows
          compact = TRUE, # thinner rows
       
  #adjust table font
  theme = reactableTheme(style = list(fontFamily = "-system-ui, -apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif")))

piracy.df %>%
  select(Interest_Drama, Piracy_use) %>%
  mutate(Interest_Drama = as.factor(Interest_Drama)) %>%
  group_by(Interest_Drama, Piracy_use) %>%
  summarise(count = n()) %>%
  pivot_wider(values_from = count, names_from = Piracy_use) %>%
  mutate(`Proportion of Non-Pirates` = `0`/(`0`+`1`)) %>%
  mutate(`Proportion of Pirates` = `1`/(`0`+`1`)) %>%
  select(Interest_Drama, `Proportion of Pirates`, `Proportion of Non-Pirates`) %>%
  pivot_longer(cols = c("Proportion of Pirates", "Proportion of Non-Pirates"),
                                                      names_to = "Piracy Use",
                                                      values_to = "Proportion of Participants") %>%
    ggplot(., aes(x = Interest_Drama, y = `Proportion of Participants`, fill = `Piracy Use`))  + geom_col(stat = "identity", width = 0.5,  position=position_dodge(0.5)) + coord_flip() + theme_stata() + scale_fill_manual(labels = c("Non-Pirate", "Pirate"), values=c("#E7B800", "#00AFBB")) + theme(axis.text.y = element_text(angle = 0, hjust = 1)) + ggtitle("Proportional Piracy by Sex Level") + xlab("User Interest") 
  
```

## Family

### Stats

```{r}
table(piracy.df$Interest_Family)
```


```{r}

temp <- piracy.df %>%
  filter(Interest_Family != 1) 

chisq.test(temp$Interest_Family, temp$Piracy_use, simulate.p.value = TRUE)

rm(temp)

piracy.df %>%
  select(Interest_Family, Piracy_use) %>%
  mutate(Interest_Family = ifelse(Interest_Family == 4 | Interest_Family == 5 , "High", "Low")) %>%
  table(.) %>%
  fisher.test(.)
  
```



### Mosaic Plot
```{r}
piracy.df %>%
  select(Interest_Family, Piracy_use) %>%
  table(.) %>%
  mosaicplot(.)


piracy.df %>%
  select(Interest_Family, Piracy_use) %>%
  mutate(Interest_Family = ifelse(Interest_Family == 4 | Interest_Family == 5, "High", "Low")) %>%
  table(.) %>%
  mosaicplot(.)
```

### Plotting

```{r}
piracy.df %>%
  select(Interest_Family, Piracy_use) %>%
  mutate(Interest_Family = as.factor(Interest_Family)) %>%
  group_by(Interest_Family, Piracy_use) %>%
  summarise(count = n()) %>%
  pivot_wider(values_from = count, names_from = Piracy_use) %>%
  mutate(Total = `0` + `1`) %>%
  mutate(`Proportion of Non-Pirates` = round((`0`/(`0`+`1`)),3)) %>%
  mutate(`Proportion of Pirates` = round((`1`/(`0`+`1`)),3)) %>%
  ungroup() %>%
  mutate(Total_All = sum(Total)) %>%
  mutate(`Proportion of Demographic` = round(Total/Total_All,3)) %>%
  select(Interest_Family,`Proportion of Demographic` ,`Proportion of Pirates`, `Proportion of Non-Pirates`)%>%
reactable(., highlight = TRUE, #allow for row to highlight when selected
          bordered = TRUE, #include borders between cells
          striped = TRUE, #striped rows
          compact = TRUE, # thinner rows
       
  #adjust table font
  theme = reactableTheme(style = list(fontFamily = "-system-ui, -apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif")))

piracy.df %>%
  select(Interest_Family, Piracy_use) %>%
  mutate(Interest_Family = as.factor(Interest_Family)) %>%
  group_by(Interest_Family, Piracy_use) %>%
  summarise(count = n()) %>%
  pivot_wider(values_from = count, names_from = Piracy_use) %>%
  mutate(`Proportion of Non-Pirates` = `0`/(`0`+`1`)) %>%
  mutate(`Proportion of Pirates` = `1`/(`0`+`1`)) %>%
  select(Interest_Family, `Proportion of Pirates`, `Proportion of Non-Pirates`) %>%
  pivot_longer(cols = c("Proportion of Pirates", "Proportion of Non-Pirates"),
                                                      names_to = "Piracy Use",
                                                      values_to = "Proportion of Participants") %>%
    ggplot(., aes(x = Interest_Family, y = `Proportion of Participants`, fill = `Piracy Use`))  + geom_col(stat = "identity", width = 0.5,  position=position_dodge(0.5)) + coord_flip() + theme_stata() + scale_fill_manual(labels = c("Non-Pirate", "Pirate"), values=c("#E7B800", "#00AFBB")) + theme(axis.text.y = element_text(angle = 0, hjust = 1)) + ggtitle("Proportional Piracy by Sex Level") + xlab("User Interest") 
  
```


## Fantasy

### Stats

```{r}
table(piracy.df$Interest_Fantasy)
```


```{r}
chisq.test(piracy.df$Interest_Fantasy, piracy.df$Piracy_use)

piracy.df %>%
  select(Interest_Fantasy, Piracy_use) %>%
  mutate(Interest_Fantasy = ifelse(Interest_Fantasy == 4 | Interest_Fantasy == 5 , "High", "Low")) %>%
  table(.) %>%
  fisher.test(.)
  
```


There is no relationship between documentary and piracy 



### Mosaic Plot
```{r}
piracy.df %>%
  select(Interest_Fantasy, Piracy_use) %>%
  table(.) %>%
  mosaicplot(.)


piracy.df %>%
  select(Interest_Fantasy, Piracy_use) %>%
  mutate(Interest_Fantasy = ifelse(Interest_Fantasy == 4 | Interest_Fantasy == 5, "High", "Low")) %>%
  table(.) %>%
  mosaicplot(.)
```

### Plotting

```{r}
piracy.df %>%
  select(Interest_Fantasy, Piracy_use) %>%
  mutate(Interest_Fantasy = as.factor(Interest_Fantasy)) %>%
  group_by(Interest_Fantasy, Piracy_use) %>%
  summarise(count = n()) %>%
  pivot_wider(values_from = count, names_from = Piracy_use) %>%
  mutate(Total = `0` + `1`) %>%
  mutate(`Proportion of Non-Pirates` = round((`0`/(`0`+`1`)),3)) %>%
  mutate(`Proportion of Pirates` = round((`1`/(`0`+`1`)),3)) %>%
  ungroup() %>%
  mutate(Total_All = sum(Total)) %>%
  mutate(`Proportion of Demographic` = round(Total/Total_All,3)) %>%
  select(Interest_Fantasy,`Proportion of Demographic` ,`Proportion of Pirates`, `Proportion of Non-Pirates`)%>%
reactable(., highlight = TRUE, #allow for row to highlight when selected
          bordered = TRUE, #include borders between cells
          striped = TRUE, #striped rows
          compact = TRUE, # thinner rows
       
  #adjust table font
  theme = reactableTheme(style = list(fontFamily = "-system-ui, -apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif")))

piracy.df %>%
  select(Interest_Fantasy, Piracy_use) %>%
  mutate(Interest_Fantasy = as.factor(Interest_Fantasy)) %>%
  group_by(Interest_Fantasy, Piracy_use) %>%
  summarise(count = n()) %>%
  pivot_wider(values_from = count, names_from = Piracy_use) %>%
  mutate(`Proportion of Non-Pirates` = `0`/(`0`+`1`)) %>%
  mutate(`Proportion of Pirates` = `1`/(`0`+`1`)) %>%
  select(Interest_Fantasy, `Proportion of Pirates`, `Proportion of Non-Pirates`) %>%
  pivot_longer(cols = c("Proportion of Pirates", "Proportion of Non-Pirates"),
                                                      names_to = "Piracy Use",
                                                      values_to = "Proportion of Participants") %>%
    ggplot(., aes(x = Interest_Fantasy, y = `Proportion of Participants`, fill = `Piracy Use`))  + geom_col(stat = "identity", width = 0.5,  position=position_dodge(0.5)) + coord_flip() + theme_stata() + scale_fill_manual(labels = c("Non-Pirate", "Pirate"), values=c("#E7B800", "#00AFBB")) + theme(axis.text.y = element_text(angle = 0, hjust = 1)) + ggtitle("Proportional Piracy by Sex Level") + xlab("User Interest") 
  
```


## Period

### Stats

```{r}
table(piracy.df$Interest_Period)
```


```{r}

temp <- piracy.df %>%
  filter(Interest_Period != 1) 

chisq.test(temp$Interest_Period, temp$Piracy_use, simulate.p.value = TRUE)

rm(temp)

piracy.df %>%
  select(Interest_Period, Piracy_use) %>%
  mutate(Interest_Period = ifelse(Interest_Period == 4 | Interest_Period == 5 , "High", "Low")) %>%
  table(.) %>%
  fisher.test(.)
  
```


There is no relationship between documentary and piracy 



### Mosaic Plot
```{r}
piracy.df %>%
  select(Interest_Period, Piracy_use) %>%
  table(.) %>%
  mosaicplot(.)


piracy.df %>%
  select(Interest_Period, Piracy_use) %>%
  mutate(Interest_Period = ifelse(Interest_Period == 4 | Interest_Period == 5, "High", "Low")) %>%
  table(.) %>%
  mosaicplot(.)
```

### Plotting

```{r}
piracy.df %>%
  select(Interest_Period, Piracy_use) %>%
  mutate(Interest_Period = as.factor(Interest_Period)) %>%
  group_by(Interest_Period, Piracy_use) %>%
  summarise(count = n()) %>%
  pivot_wider(values_from = count, names_from = Piracy_use) %>%
  mutate(Total = `0` + `1`) %>%
  mutate(`Proportion of Non-Pirates` = round((`0`/(`0`+`1`)),3)) %>%
  mutate(`Proportion of Pirates` = round((`1`/(`0`+`1`)),3)) %>%
  ungroup() %>%
  mutate(Total_All = sum(Total)) %>%
  mutate(`Proportion of Demographic` = round(Total/Total_All,3)) %>%
  select(Interest_Period,`Proportion of Demographic` ,`Proportion of Pirates`, `Proportion of Non-Pirates`)%>%
reactable(., highlight = TRUE, #allow for row to highlight when selected
          bordered = TRUE, #include borders between cells
          striped = TRUE, #striped rows
          compact = TRUE, # thinner rows
       
  #adjust table font
  theme = reactableTheme(style = list(fontFamily = "-system-ui, -apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif")))

piracy.df %>%
  select(Interest_Period, Piracy_use) %>%
  mutate(Interest_Period = as.factor(Interest_Period)) %>%
  group_by(Interest_Period, Piracy_use) %>%
  summarise(count = n()) %>%
  pivot_wider(values_from = count, names_from = Piracy_use) %>%
  mutate(`Proportion of Non-Pirates` = `0`/(`0`+`1`)) %>%
  mutate(`Proportion of Pirates` = `1`/(`0`+`1`)) %>%
  select(Interest_Period, `Proportion of Pirates`, `Proportion of Non-Pirates`) %>%
  pivot_longer(cols = c("Proportion of Pirates", "Proportion of Non-Pirates"),
                                                      names_to = "Piracy Use",
                                                      values_to = "Proportion of Participants") %>%
    ggplot(., aes(x = Interest_Period, y = `Proportion of Participants`, fill = `Piracy Use`))  + geom_col(stat = "identity", width = 0.5,  position=position_dodge(0.5)) + coord_flip() + theme_stata() + scale_fill_manual(labels = c("Non-Pirate", "Pirate"), values=c("#E7B800", "#00AFBB")) + theme(axis.text.y = element_text(angle = 0, hjust = 1)) + ggtitle("Proportional Piracy by Sex Level") + xlab("User Interest") 
  
```

## Romance

### Stats

```{r}
table(piracy.df$Interest_Romance)
```


```{r}

temp <- piracy.df %>%
  filter(Interest_Romance != 1) 

chisq.test(temp$Interest_Romance, temp$Piracy_use, simulate.p.value = TRUE)

rm(temp)

piracy.df %>%
  select(Interest_Romance, Piracy_use) %>%
  mutate(Interest_Romance = ifelse(Interest_Romance == 4 | Interest_Romance == 5 , "High", "Low")) %>%
  table(.) %>%
  fisher.test(.)
  
```

There is an association between interest in Romance and Piracy

High Interest in Romance are less likely to use piracy (odds are about 0.5 of those who have a lower interest in Romance)

### Mosaic Plot
```{r}
piracy.df %>%
  select(Interest_Romance, Piracy_use) %>%
  filter(Interest_Romance != 1) %>%
  table(.) %>%
  mosaicplot(.)


piracy.df %>%
  select(Interest_Romance, Piracy_use) %>%
  mutate(Interest_Romance = ifelse(Interest_Romance == 4 | Interest_Romance == 5, "High", "Low")) %>%
  table(.) %>%
  mosaicplot(.)
```

### Plotting

```{r}
piracy.df %>%
  select(Interest_Romance, Piracy_use) %>%
  mutate(Interest_Romance = as.factor(Interest_Romance)) %>%
  group_by(Interest_Romance, Piracy_use) %>%
  summarise(count = n()) %>%
  pivot_wider(values_from = count, names_from = Piracy_use) %>%
  mutate(Total = `0` + `1`) %>%
  mutate(`Proportion of Non-Pirates` = round((`0`/(`0`+`1`)),3)) %>%
  mutate(`Proportion of Pirates` = round((`1`/(`0`+`1`)),3)) %>%
  ungroup() %>%
  mutate(Total_All = sum(Total)) %>%
  mutate(`Proportion of Demographic` = round(Total/Total_All,3)) %>%
  select(Interest_Romance,`Proportion of Demographic` ,`Proportion of Pirates`, `Proportion of Non-Pirates`)%>%
reactable(., highlight = TRUE, #allow for row to highlight when selected
          bordered = TRUE, #include borders between cells
          striped = TRUE, #striped rows
          compact = TRUE, # thinner rows
       
  #adjust table font
  theme = reactableTheme(style = list(fontFamily = "-system-ui, -apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif")))

piracy.df %>%
  select(Interest_Romance, Piracy_use) %>%
  mutate(Interest_Romance = as.factor(Interest_Romance)) %>%
  group_by(Interest_Romance, Piracy_use) %>%
  summarise(count = n()) %>%
  pivot_wider(values_from = count, names_from = Piracy_use) %>%
  mutate(`Proportion of Non-Pirates` = `0`/(`0`+`1`)) %>%
  mutate(`Proportion of Pirates` = `1`/(`0`+`1`)) %>%
  select(Interest_Romance, `Proportion of Pirates`, `Proportion of Non-Pirates`) %>%
  pivot_longer(cols = c("Proportion of Pirates", "Proportion of Non-Pirates"),
                                                      names_to = "Piracy Use",
                                                      values_to = "Proportion of Participants") %>%
    ggplot(., aes(x = Interest_Romance, y = `Proportion of Participants`, fill = `Piracy Use`))  + geom_col(stat = "identity", width = 0.5,  position=position_dodge(0.5)) + coord_flip() + theme_stata() + scale_fill_manual(labels = c("Non-Pirate", "Pirate"), values=c("#E7B800", "#00AFBB")) + theme(axis.text.y = element_text(angle = 0, hjust = 1)) + ggtitle("Proportional Piracy by Sex Level") + xlab("User Interest") 
  
```

### Demographics


#### Age
```{r}
table(piracy.df$Interest_Romance, piracy.df$Age)
```

```{r}
temp <- piracy.df %>%
  filter(Interest_Romance != 1) %>%
  filter(Interest_Romance != 2 & Age != 4) %>%
  filter(Interest_Romance != 3 & Age != 3) %>%
  filter(Interest_Romance != 3 & Age != 4) 


chisq.test(temp$Interest_Romance, temp$Age, simulate.p.value = TRUE)

rm(temp)

piracy.df %>%
  select(Interest_Romance, Age) %>%
  mutate(Interest_Romance = ifelse(Interest_Romance == 4 | Interest_Romance == 5 , "High", "Low")) %>%
  mutate(Age = ifelse(Age == 1 | Age == 2 , "Younger", "Older")) %>%
  table(.) %>%
  fisher.test(.)
```

The odds of younger people having a high interest in romance is about 60% lower than older people

#### Sex
```{r}
table(piracy.df$Interest_Romance, piracy.df$Sex)
```

```{r}
# temp <- piracy.df %>%
#   filter(Interest_Romance != 1) %>%
#   filter(Interest_Romance != 2 & Age != 4) %>%
#   filter(Interest_Romance != 3 & Age != 3) %>%
#   filter(Interest_Romance != 3 & Age != 4) 
# 
# 
# chisq.test(temp$Interest_Romance, temp$Age, simulate.p.value = TRUE)
# 
# rm(temp)

piracy.df %>%
  select(Interest_Romance, Sex) %>%
  mutate(Interest_Romance = ifelse(Interest_Romance == 4 | Interest_Romance == 5 , "High", "Low")) %>%
  table(.) %>%
  fisher.test(.)
```

The odds of men people having a high interest in romance is about 82% lower than women 

#### Education
```{r}
table(piracy.df$Interest_Romance, piracy.df$Education)
```

```{r}

piracy.df %>%
  select(Education, Interest_Romance) %>%
  mutate(Interest_Romance = ifelse(Interest_Romance == 4 | Interest_Romance == 5, "High", "Low")) %>%
  group_by(Education, Interest_Romance) %>%
  summarise(count = n(), .groups = "drop") %>%
  pivot_wider(values_from = count, names_from = Interest_Romance) %>%
  mutate(Sum_High = sum(High, na.rm = TRUE), Sum_Low = sum(Low, na.rm = TRUE)) %>%
  mutate(propLow = Low/Sum_Low) %>%
  mutate(propHigh = High/Sum_High) %>%
  select(Education, propLow, propHigh)



temp <- piracy.df %>%
  filter(Interest_Romance != 1) %>%
  filter(Interest_Romance != 2 & Education != 4) %>%
  filter(Interest_Romance != 3 & Age != 3) %>%
  filter(Interest_Romance != 3 & Age != 4)


chisq.test(temp$Interest_Romance, temp$Age, simulate.p.value = TRUE)

rm(temp)

piracy.df %>%
  select(Interest_Romance, Education) %>%
  mutate(Interest_Romance = ifelse(Interest_Romance == 4 | Interest_Romance == 5 , "High", "Low")) %>%
  table(.) %>%
  fisher.test(.)
```

The odds of younger people having a high interest in romance is about 60% lower than older people

## Science Fiction

### Stats

```{r}
table(piracy.df$Interest_Science_fiction)
```


```{r}

chisq.test(piracy.df$Interest_Science_fiction, piracy.df$Piracy_use, simulate.p.value = TRUE)


piracy.df %>%
  select(Interest_Science_fiction, Piracy_use) %>%
  mutate(Interest_Science_fiction = ifelse(Interest_Science_fiction == 4 | Interest_Science_fiction == 5 , "High", "Low")) %>%
  table(.) %>%
  fisher.test(.)
  
```


There is no relationship between documentary and piracy 



### Mosaic Plot
```{r}
piracy.df %>%
  select(Interest_Science_fiction, Piracy_use) %>%
  table(.) %>%
  mosaicplot(.)


piracy.df %>%
  select(Interest_Science_fiction, Piracy_use) %>%
  mutate(Interest_Science_fiction = ifelse(Interest_Science_fiction == 4 | Interest_Science_fiction == 5, "High", "Low")) %>%
  table(.) %>%
  mosaicplot(.)
```

### Plotting

```{r}
piracy.df %>%
  select(Interest_Science_fiction, Piracy_use) %>%
  mutate(Interest_Science_fiction = as.factor(Interest_Science_fiction)) %>%
  group_by(Interest_Science_fiction, Piracy_use) %>%
  summarise(count = n()) %>%
  pivot_wider(values_from = count, names_from = Piracy_use) %>%
  mutate(Total = `0` + `1`) %>%
  mutate(`Proportion of Non-Pirates` = round((`0`/(`0`+`1`)),3)) %>%
  mutate(`Proportion of Pirates` = round((`1`/(`0`+`1`)),3)) %>%
  ungroup() %>%
  mutate(Total_All = sum(Total)) %>%
  mutate(`Proportion of Demographic` = round(Total/Total_All,3)) %>%
  select(Interest_Science_fiction,`Proportion of Demographic` ,`Proportion of Pirates`, `Proportion of Non-Pirates`)%>%
reactable(., highlight = TRUE, #allow for row to highlight when selected
          bordered = TRUE, #include borders between cells
          striped = TRUE, #striped rows
          compact = TRUE, # thinner rows
       
  #adjust table font
  theme = reactableTheme(style = list(fontFamily = "-system-ui, -apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif")))

piracy.df %>%
  select(Interest_Science_fiction, Piracy_use) %>%
  mutate(Interest_Science_fiction = as.factor(Interest_Science_fiction)) %>%
  group_by(Interest_Science_fiction, Piracy_use) %>%
  summarise(count = n()) %>%
  pivot_wider(values_from = count, names_from = Piracy_use) %>%
  mutate(`Proportion of Non-Pirates` = `0`/(`0`+`1`)) %>%
  mutate(`Proportion of Pirates` = `1`/(`0`+`1`)) %>%
  select(Interest_Science_fiction, `Proportion of Pirates`, `Proportion of Non-Pirates`) %>%
  pivot_longer(cols = c("Proportion of Pirates", "Proportion of Non-Pirates"),
                                                      names_to = "Piracy Use",
                                                      values_to = "Proportion of Participants") %>%
    ggplot(., aes(x = Interest_Science_fiction, y = `Proportion of Participants`, fill = `Piracy Use`))  + geom_col(stat = "identity", width = 0.5,  position=position_dodge(0.5)) + coord_flip() + theme_stata() + scale_fill_manual(labels = c("Non-Pirate", "Pirate"), values=c("#E7B800", "#00AFBB")) + theme(axis.text.y = element_text(angle = 0, hjust = 1)) + ggtitle("Proportional Piracy by Sex Level") + xlab("User Interest") 
  
```

## Terror

### Stats

```{r}
table(piracy.df$Interest_Terror)
```


```{r}

chisq.test(piracy.df$Interest_Terror, piracy.df$Piracy_use, simulate.p.value = TRUE)

piracy.df %>%
  select(Interest_Terror, Piracy_use) %>%
  mutate(Interest_Terror = ifelse(Interest_Terror == 4 | Interest_Terror == 5 , "High", "Low")) %>%
  table(.) %>%
  fisher.test(.)
  
```


There is no relationship between documentary and piracy 



### Mosaic Plot
```{r}
piracy.df %>%
  select(Interest_Terror, Piracy_use) %>%
  table(.) %>%
  mosaicplot(.)


piracy.df %>%
  select(Interest_Terror, Piracy_use) %>%
  mutate(Interest_Terror = ifelse(Interest_Terror == 4 | Interest_Terror == 5, "High", "Low")) %>%
  table(.) %>%
  mosaicplot(.)
```

### Plotting

```{r}
piracy.df %>%
  select(Interest_Terror, Piracy_use) %>%
  mutate(Interest_Terror = as.factor(Interest_Terror)) %>%
  group_by(Interest_Terror, Piracy_use) %>%
  summarise(count = n()) %>%
  pivot_wider(values_from = count, names_from = Piracy_use) %>%
  mutate(Total = `0` + `1`) %>%
  mutate(`Proportion of Non-Pirates` = round((`0`/(`0`+`1`)),3)) %>%
  mutate(`Proportion of Pirates` = round((`1`/(`0`+`1`)),3)) %>%
  ungroup() %>%
  mutate(Total_All = sum(Total)) %>%
  mutate(`Proportion of Demographic` = round(Total/Total_All,3)) %>%
  select(Interest_Terror,`Proportion of Demographic` ,`Proportion of Pirates`, `Proportion of Non-Pirates`)%>%
reactable(., highlight = TRUE, #allow for row to highlight when selected
          bordered = TRUE, #include borders between cells
          striped = TRUE, #striped rows
          compact = TRUE, # thinner rows
       
  #adjust table font
  theme = reactableTheme(style = list(fontFamily = "-system-ui, -apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif")))

piracy.df %>%
  select(Interest_Terror, Piracy_use) %>%
  mutate(Interest_Terror = as.factor(Interest_Terror)) %>%
  group_by(Interest_Terror, Piracy_use) %>%
  summarise(count = n()) %>%
  pivot_wider(values_from = count, names_from = Piracy_use) %>%
  mutate(`Proportion of Non-Pirates` = `0`/(`0`+`1`)) %>%
  mutate(`Proportion of Pirates` = `1`/(`0`+`1`)) %>%
  select(Interest_Terror, `Proportion of Pirates`, `Proportion of Non-Pirates`) %>%
  pivot_longer(cols = c("Proportion of Pirates", "Proportion of Non-Pirates"),
                                                      names_to = "Piracy Use",
                                                      values_to = "Proportion of Participants") %>%
    ggplot(., aes(x = Interest_Terror, y = `Proportion of Participants`, fill = `Piracy Use`))  + geom_col(stat = "identity", width = 0.5,  position=position_dodge(0.5)) + coord_flip() + theme_stata() + scale_fill_manual(labels = c("Non-Pirate", "Pirate"), values=c("#E7B800", "#00AFBB")) + theme(axis.text.y = element_text(angle = 0, hjust = 1)) + ggtitle("Proportional Piracy by Sex Level") + xlab("User Interest") 
  
```

## Thriller

### Stats

```{r}
table(piracy.df$Interest_Thriller)
```


```{r}

chisq.test(piracy.df$Interest_Thriller, piracy.df$Piracy_use, simulate.p.value = TRUE)

piracy.df %>%
  select(Interest_Thriller, Piracy_use) %>%
  mutate(Interest_Thriller = ifelse(Interest_Thriller == 4 | Interest_Thriller == 5 , "High", "Low")) %>%
  table(.) %>%
  fisher.test(.)
  
```

There is a relationship between user interest in thriller and piracy

High Interest in Thriller are more likely to use piracy by an odds of 1.7 more than those with a low interest in thriller


### Mosaic Plot
```{r}
piracy.df %>%
  select(Interest_Romance, Piracy_use) %>%
  table(.) %>%
  mosaicplot(.)


piracy.df %>%
  select(Interest_Romance, Piracy_use) %>%
  mutate(Interest_Romance = ifelse(Interest_Romance == 4 | Interest_Romance == 5, "High", "Low")) %>%
  table(.) %>%
  mosaicplot(.)
```

### Plotting

```{r}
piracy.df %>%
  select(Interest_Romance, Piracy_use) %>%
  mutate(Interest_Romance = as.factor(Interest_Romance)) %>%
  group_by(Interest_Romance, Piracy_use) %>%
  summarise(count = n()) %>%
  pivot_wider(values_from = count, names_from = Piracy_use) %>%
  mutate(Total = `0` + `1`) %>%
  mutate(`Proportion of Non-Pirates` = round((`0`/(`0`+`1`)),3)) %>%
  mutate(`Proportion of Pirates` = round((`1`/(`0`+`1`)),3)) %>%
  ungroup() %>%
  mutate(Total_All = sum(Total)) %>%
  mutate(`Proportion of Demographic` = round(Total/Total_All,3)) %>%
  select(Interest_Romance,`Proportion of Demographic` ,`Proportion of Pirates`, `Proportion of Non-Pirates`)%>%
reactable(., highlight = TRUE, #allow for row to highlight when selected
          bordered = TRUE, #include borders between cells
          striped = TRUE, #striped rows
          compact = TRUE, # thinner rows
       
  #adjust table font
  theme = reactableTheme(style = list(fontFamily = "-system-ui, -apple-system, BlinkMacSystemFont, Segoe UI, Helvetica, Arial, sans-serif")))

piracy.df %>%
  select(Interest_Romance, Piracy_use) %>%
  mutate(Interest_Romance = as.factor(Interest_Romance)) %>%
  group_by(Interest_Romance, Piracy_use) %>%
  summarise(count = n()) %>%
  pivot_wider(values_from = count, names_from = Piracy_use) %>%
  mutate(`Proportion of Non-Pirates` = `0`/(`0`+`1`)) %>%
  mutate(`Proportion of Pirates` = `1`/(`0`+`1`)) %>%
  select(Interest_Romance, `Proportion of Pirates`, `Proportion of Non-Pirates`) %>%
  pivot_longer(cols = c("Proportion of Pirates", "Proportion of Non-Pirates"),
                                                      names_to = "Piracy Use",
                                                      values_to = "Proportion of Participants") %>%
    ggplot(., aes(x = Interest_Romance, y = `Proportion of Participants`, fill = `Piracy Use`))  + geom_col(stat = "identity", width = 0.5,  position=position_dodge(0.5)) + coord_flip() + theme_stata() + scale_fill_manual(labels = c("Non-Pirate", "Pirate"), values=c("#E7B800", "#00AFBB")) + theme(axis.text.y = element_text(angle = 0, hjust = 1)) + ggtitle("Proportional Piracy by Sex Level") + xlab("User Interest") 
  
```
### Demographics

#### Age
```{r}
table(piracy.df$Interest_Thriller, piracy.df$Age)
```

```{r}
# temp <- piracy.df %>%
#   filter(Interest_Thriller != 1) %>%
#   filter(Interest_Thriller != 2 & Age != 1) %>%
#   filter(Interest_Thriller != 2 & Age != 3) %>%
#   filter(Interest_Thriller != 2 & Age != 4) 
# 
# temp
# 
# chisq.test(temp$Interest_Romance, temp$Age, simulate.p.value = TRUE)

#rm(temp)

piracy.df %>%
  select(Interest_Romance, Age) %>%
  mutate(Interest_Romance = ifelse(Interest_Romance == 4 | Interest_Romance == 5 , "High", "Low")) %>%
  mutate(Age = ifelse(Age == 1 | Age == 2 , "Younger", "Older")) %>%
  table(.) %>%
  fisher.test(.)
```

The odds of younger people having a high interest in romance is about 70% lower than older people

#### Sex
```{r}
table(piracy.df$Interest_Thriller, piracy.df$Sex)
```

```{r}

temp1 <- piracy.df %>%
  filter(Sex == 1) %>%
  sample_n(200)

temp2 <- piracy.df %>%
  filter(Sex == 2) %>%
  sample_n(200)

temp1 <- rbind(temp1, temp2)
  

temp <- temp1 %>%
  filter(Interest_Thriller != 1) 
  
  
chisq.test(temp$Interest_Thriller, temp$Sex, simulate.p.value = TRUE)

rm(temp)

temp1 %>%
  select(Interest_Thriller, Sex) %>%
  mutate(Interest_Thriller = ifelse(Interest_Thriller == 4 | Interest_Thriller == 5 , "High", "Low")) %>%
  table(.) %>%
  fisher.test(.)
```
There is a relationship between Age and whether they watch Thriller 


## All Genres

```{r}
i = 7

for (var in colnames(piracy_allfactors[7:18])) {

#go through each column and make a matrix of the proportion of piracy and n for all genres  
temp.matrix <- piracy_allfactors %>%
    group_by(piracy_allfactors[[i]], Piracy_use) %>%   
    tally() %>%
    pivot_wider(names_from = Piracy_use, values_from = n) %>%
    mutate(Pirate = ifelse(is.na(Pirate),0,Pirate)) %>%
    mutate(`Non-Pirate` = ifelse(is.na(`Non-Pirate`), 0, `Non-Pirate`))%>%
    mutate(Prop = Pirate/(Pirate + `Non-Pirate`)) %>%
    mutate(N = Pirate + `Non-Pirate`)

#save the proportion of piracy and n as vectors
p.g.plot <- as.vector(temp.matrix$Prop)
n.plot <- as.vector(temp.matrix$N)

#save each genre proportion and n vector in the global environment
eval(parse(text = paste0('prop', var, 
                           ' <- p.g.plot')))

eval(parse(text = paste0('n', var, 
                           ' <- n.plot')))
  
i = i + 1
}

#put all the proportions in the one vector
check.genre <- c(propInterest_Action, propInterest_Comedy, propInterest_Disaster, propInterest_Documentary, propInterest_Drama, propInterest_Family, propInterest_Fantasy, propInterest_Period, propInterest_Romance, propInterest_Science_fiction, propInterest_Terror, propInterest_Thriller)

#put all the n values in one vector
n.genre <- c(nInterest_Action, nInterest_Comedy, nInterest_Disaster, nInterest_Documentary, nInterest_Drama, nInterest_Family, nInterest_Fantasy, nInterest_Period, nInterest_Romance, nInterest_Science_fiction, nInterest_Terror, nInterest_Thriller)

#recreate the dataset with the original data labels for interest level and genre
intlev <- rep(c("Interested", "Neutral", "Slightly Interested", "Uninterested", "Very Interested", "Very Uninterested"),12)
genre.name <- c(rep("Action", 6), rep("Comedy", 6), rep("Disaster",6), rep("Documentry",6),  rep("Drama", 6), rep("Family", 6), rep("Fantasy", 6), rep("Period", 6), rep("Romance", 6), rep("SciFi", 6), rep("Terror", 6), rep("Thriller", 6))




```


```{r}
#create the final data frame
heatmap.df <- data.frame(genre.name, intlev, check.genre, n.genre)

#rename columns
names(heatmap.df)[names(heatmap.df) == "genre.name"] <- "Genre"
names(heatmap.df)[names(heatmap.df) == "intlev"] <- "Interest_Level"
names(heatmap.df)[names(heatmap.df) == "check.genre"] <- "Proportion"
names(heatmap.df)[names(heatmap.df) == "n.genre"] <- "N"

#make sure interest_level column factors are in the right order
heatmap.df$Interest_Level <- factor(heatmap.df$Interest_Level, 
                            levels = c("Very Uninterested", "Uninterested", "Neutral", 
                                       "Slightly Interested", "Interested", "Very Interested"))

#find the average proportion of each row(genre) in the heatmap
temp <- heatmap.df %>%
  group_by(Genre) %>%
  summarise(Average = mean(Proportion), N = sum(N)) %>%
  pivot_longer(cols = c("Average"),
               values_to = "Proportion", names_to = "Interest_Level")

#filter out rows that have less than N so that they will be grayed out in the heat map. 
heatmap.df <- heatmap.df %>%
  mutate(Proportion = ifelse(N < 5, NA, Proportion)) %>%
  #add in the extra row about the average proportion
  rbind(., temp)

#remove because no longer needed. 
rm(temp)

```



###Heat Map
```{r}
ggplot(heatmap.df, aes(x = Interest_Level, y = Genre, fill = Proportion)) +
  geom_tile(color = "white", size = 1) +
  scale_fill_gradientn(colors = c("darkgreen" ,"yellow", "darkred", na.value="lightgrey"),limits = c(0, 1)) +
  theme_minimal() +
  geom_label(aes(label =  paste0(round(Proportion, 2), "\n", "n: ", N)), fill = "white", color = "black", size = 2.5) +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggtitle("Proportion of Piracy per User Interest Level in Genre") + 
  xlab("Interest Level")
  
```


# Platforms and Genres

```{r}
rom_thriller_prop <- read.csv("justplatforms2.csv")
```

## Romance Prop

### Normality


```{r}
# add in the romance and thriller proportion information
merge(x = piracy_factor, y = rom_thriller_prop, by = "allplatforms", all.x = TRUE) 


merge(x = piracy_factor, y = rom_thriller_prop, by = "allplatforms", all.x = TRUE) %>%
  select(5, 20) %>%
  filter(Piracy_use == "Pirate") %>%
  ggplot(., aes(x = RomanceProp)) + geom_histogram(aes(y = ..density..), 
  bins = 10, fill = "skyblue", color = "black", alpha = 0.7) + geom_density(color = "red", size = 1) + xlab("Proportion of Romance")  + theme_stata() + ggtitle("Normality of Proportion of Romance Content Amongst Pirates")

merge(x = piracy_factor, y = rom_thriller_prop, by = "allplatforms", all.x = TRUE) %>%
  select(5, 20) %>%
  filter(Piracy_use == "Non-Pirate") %>%
  ggplot(., aes(x = RomanceProp)) + geom_histogram(aes(y = ..density..), 
  bins = 10, fill = "skyblue", color = "black", alpha = 0.7) + geom_density(color = "red", size = 1) + xlab("Proportion of Romance")  + theme_stata() + ggtitle("Normality of Proportion of Romance Content Amongst Non-Pirates")
  



```

```{r}
# Shapiro-Wilk normality test for pirates

merge(x = piracy_factor, y = rom_thriller_prop, by = "allplatforms", all.x = TRUE) %>%
  with(., shapiro.test(RomanceProp[Piracy_use == "Pirate"]))

# Shapiro-Wilk normality test for non-pirates
merge(x = piracy_factor, y = rom_thriller_prop, by = "allplatforms", all.x = TRUE) %>%
  with(., shapiro.test(RomanceProp[Piracy_use == "Non-Pirate"]))
```
Non-Normal Distribution as expected

### Boxplot

```{r}

p <- merge(x = piracy_factor, y = rom_thriller_prop, by = "allplatforms", all.x = TRUE)  %>%
  ggboxplot(., x = "Piracy_use", y = "RomanceProp",
          color = "Piracy_use", palette = c("#00AFBB", "#E7B800"),
        ylab = "Proportion of Romance Content", xlab = "Piracy Use")  + theme_stata() + ggtitle("Romance Content Availability and Piracy Use") + theme(legend.position="none")
  

ggplotly(p) 
```



### T.Test
```{r}
merge(x = piracy_factor, y = rom_thriller_prop, by = "allplatforms", all.x = TRUE)  %>%
  var.test(RomanceProp ~ Piracy_use, data = .)


merge(x = piracy_factor, y = rom_thriller_prop, by = "allplatforms", all.x = TRUE)  %>%
  t.test(RomanceProp ~ Piracy_use, data = ., var.equal = FALSE)
```

There is a difference between the average proportion of romance that Pirates and Non-Pirates have access to. Non-Pirates have access to slightly more romance content than Pirates do.

```{r}
merge(x = piracy_factor, y = rom_thriller_prop, by = "allplatforms", all.x = TRUE)  %>%
  select(allplatforms, RomanceProp, Piracy_use) %>%
  group_by(allplatforms, RomanceProp, Piracy_use) %>%
  summarise(count = n()) %>%
  pivot_wider(names_from = Piracy_use, values_from = count) %>%
  mutate(`Non-Pirate` = ifelse(is.na(`Non-Pirate`), 0, `Non-Pirate`)) %>%
  mutate(`Pirate` = ifelse(is.na(`Pirate`), 0, `Pirate`)) %>%
  mutate(PropPirate = Pirate/(`Non-Pirate`+Pirate)) %>%
  select(allplatforms, RomanceProp, PropPirate) %>%
  arrange(desc(RomanceProp)) %>%
  filter(allplatforms %in% top10factors$allplatforms) 

  


```



## Thriller Prop

### Normality


```{r}

merge(x = piracy_factor, y = rom_thriller_prop, by = "allplatforms", all.x = TRUE) %>%
  select(5, 21) %>%
  filter(Piracy_use == "Pirate") %>%
  ggplot(., aes(x = ThrillerProp)) + geom_histogram(aes(y = ..density..), 
  bins = 10, fill = "skyblue", color = "black", alpha = 0.7) + geom_density(color = "red", size = 1) + xlab("Proportion of Thriller")  + theme_stata() + ggtitle("Normality of Proportion of Thriller Content Amongst Pirates")

merge(x = piracy_factor, y = rom_thriller_prop, by = "allplatforms", all.x = TRUE) %>%
  select(5, 21) %>%
  filter(Piracy_use == "Non-Pirate") %>%
  ggplot(., aes(x = ThrillerProp)) + geom_histogram(aes(y = ..density..), 
  bins = 10, fill = "skyblue", color = "black", alpha = 0.7) + geom_density(color = "red", size = 1) + xlab("Proportion of Thriller")  + theme_stata() + ggtitle("Normality of Proportion of Thriller Content Amongst Non-Pirates")
  



```

```{r}
# Shapiro-Wilk normality test for pirates

merge(x = piracy_factor, y = rom_thriller_prop, by = "allplatforms", all.x = TRUE) %>%
  with(., shapiro.test(ThrillerProp[Piracy_use == "Pirate"]))

# Shapiro-Wilk normality test for non-pirates
merge(x = piracy_factor, y = rom_thriller_prop, by = "allplatforms", all.x = TRUE) %>%
  with(., shapiro.test(ThrillerProp[Piracy_use == "Non-Pirate"]))
```
Non-Normal Distribution as expected

### Boxplot

```{r}

p <- merge(x = piracy_factor, y = rom_thriller_prop, by = "allplatforms", all.x = TRUE)  %>%
  ggboxplot(., x = "Piracy_use", y = "ThrillerProp",
          color = "Piracy_use", palette = c("#00AFBB", "#E7B800"),
        ylab = "Proportion of Thriller Content", xlab = "Piracy Use")  + theme_stata() + ggtitle("Thriller Content Availability and Piracy Use") + theme(legend.position="none")
  

ggplotly(p) 
```



### T.Test
```{r}
merge(x = piracy_factor, y = rom_thriller_prop, by = "allplatforms", all.x = TRUE)  %>%
  var.test(ThrillerProp ~ Piracy_use, data = .)


merge(x = piracy_factor, y = rom_thriller_prop, by = "allplatforms", all.x = TRUE)  %>%
  t.test(ThrillerProp ~ Piracy_use, data = ., var.equal = FALSE)

```
There is a difference between the average proportion of thriller that Pirates and Non-Pirates have access to. Non-Pirates have access to slightly more thriller content than Pirates do.

```{r}
merge(x = piracy_factor, y = rom_thriller_prop, by = "allplatforms", all.x = TRUE)  %>%
  select(allplatforms, ThrillerProp, Piracy_use) %>%
  group_by(allplatforms, ThrillerProp, Piracy_use) %>%
  summarise(count = n()) %>%
  pivot_wider(names_from = Piracy_use, values_from = count) %>%
  mutate(`Non-Pirate` = ifelse(is.na(`Non-Pirate`), 0, `Non-Pirate`)) %>%
  mutate(`Pirate` = ifelse(is.na(`Pirate`), 0, `Pirate`)) %>%
  mutate(PropPirate = Pirate/(`Non-Pirate`+Pirate)) %>%
  select(allplatforms, ThrillerProp, PropPirate) %>%
  arrange(desc(ThrillerProp)) %>%
  filter(allplatforms %in% top10factors$allplatforms) 

```



# Dimension Reduction

## FAMD
```{r}
famd.piracy <- FAMD(piracy_factor, graph = FALSE)
summary(famd.piracy)
```

## Plot
```{r}
fviz_eig(famd.piracy, addlabels = TRUE, hjust = -0.3, linecolor = "red", barfill = "darkblue", barcolor = "darkblue") + ylim(0,5) + theme_stata() + labs(title = "Variances - FAMD", x = "Principal Components", y = "% of Explained Variances")
```



